Variational Monte Carlo on Bosonic Systems

### 2018-04-05 project_1/article/article.tex
Spell check section on drift force

    \subsection{The drift force}
        A disadvantage in the use of the brute force Metropolis-Hastings
        algorithm is that we might be spending much computational resources in
        an uninteresting part of configuration space. To make smarter moves we
        will use the Metropolis-Hastings algorithm with the additions of
        \emph{Importance Sampling}  (which will be discussed in due time). This
        alteration of the algorithm is dependent on the \emph{drift force} of
        the system\footnote{Also known as the \emph{quantum force}.}.
        \begin{align}
            \vf{F}(\vf{r})
            &=
            \sum_{k = 1}^N
            \vf{F}_k(\vf{r})
            =
            \sum_{k = 1}^N
            \frac{2\nabla_k\Psi_T(\vf{r})}{\Psi_T(\vf{r})}.
            \label{eq:drift_force}
        \end{align}
        Using this expression we are able to move towards parts of
        configuration space where the gradient increases or decreases yielding a
        better choice of movements. We will mainly be interested in the drift
        force of a single particle $k$ as the Monte Carlo sampling involves
        choosing a single particle at a time.

>>>>

    \subsection{The drift force}
        A disadvantage in the use of the brute force Metropolis-Hastings
        algorithm is that we might be spending much computational resources in
        an uninteresting part of configuration space. To make smarter moves we
        will add importance sampling (which will be discussed in due time) to
        the algorithm. This alteration of the algorithm needs a new quantity
        called the \emph{drift force} of the system\footnote{Also known as the
        \emph{quantum force}.}.
        \begin{align}
            \vf{F}(\vf{r})
            &=
            \sum_{k = 1}^N
            \vf{F}_k(\vf{r})
            =
            \sum_{k = 1}^N
            \frac{2\nabla_k\Psi_T(\vf{r})}{\Psi_T(\vf{r})}.
            \label{eq:drift_force}
        \end{align}
        Using the drift force we are able to move towards more interesting parts
        of configuration space as we are following the gradient of the
        wavefunction. We will mainly be interested in the drift force of a
        single particle $k$ as the Monte Carlo sampling involves choosing a
        single particle at a time.
